Efficient and Robust N-Mesh Boolean Operations Using Hybrid Representations

### 2017-03-06 paper.tex
before delete plane based implementation itemize
before merge with hongbo

\documentclass[10pt,journal,compsoc]{IEEEtran}

@@

@@

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\floatname{algorithm}{Algorithm}

\begin{document}
\title{Efficient and Robust Plane-Based Boolean Operations on N Meshes}
\author{%Rui~Wang,~
        %Xudong~Jiang,~
        %Hongbo~Fu,~
        %Ping~Li,~
        %Bin~Sheng~and
        %Enhua~Wu
\IEEEcompsocitemizethanks{

@@

\IEEEcompsocthanksitem X. Jiang is with Autodesk China Research \& Development Center. Email: xudong.jiang@autodesk.com

@@

\IEEEcompsocthanksitem P. Li is with the Department of Mathematics and Information Technology, The Hong Kong Institute of Education. Email: pli@ied.edu.hk

@@

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{xudong}}]{Xudong Jiang}
received his Master degree in Computer Science from Shanghai Jiao Tong University in 2014. He is currently working in Autodesk China Research \& Development Center. His research interest includes computer-aided geometric design and solid modeling.
\end{IEEEbiography}

@@

>>>>

\documentclass[10pt,final,compsoc]{IEEEtran}

@@

\usepackage{amsthm}

@@

\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
\floatname{algorithm}{Algorithm}
%\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\newtheorem{theorem}{Theorem}

\begin{document}
\title{Efficient and Robust N-Mesh Boolean Operations Using Hybrid Representations}
\author{
        Rui~Wang,~
        Bin~Sheng~
        Hongbo~Fu,~
        Ping~Li,~and~
        Enhua~Wu
\IEEEcompsocitemizethanks{

@@

%\IEEEcompsocthanksitem X. Jiang is with Autodesk China Research \& Development Center. Email: xudong.jiang@autodesk.com

@@

\IEEEcompsocthanksitem P. Li is with the Department of Mathematics and Information Technology, The Hong Kong Institute of Education. Email: pli@eduhk.hk

@@

% if you will not have a photo at all:
% \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{xudong}}]{Xudong Jiang}
% received his Master degree in Computer Science from Shanghai Jiao Tong University in 2014. He is currently working in Autodesk China Research \& Development Center. His research interest includes computer-aided geometric design and solid modeling.
% \end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{liping}}]{Li Ping}
 received his Ph.D. from The Chinese University of Hong Kong. He is currently a Lecturer at The Education University of Hong Kong. His research interests include image/video stylization, learning analytics, big data visualization, and creative media.
\end{IEEEbiography}

### 2017-03-06 tex/exp.tex
before merge with hongbo

\begin{figure}[t]
\centering
\includegraphics[width=3in]{perturb}
\caption{After perturbation, the self-union of \emph{Bunny} with QuickCSG still suffers from topology problem. The green boundary faces indicate topological deficiencies.}
%
\label{fig:boundaryedge}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3in]{buddalion}
\caption{ Results from $Budda\cup Lion$: a) incorrect result using CGAL, b) incorrect result using Cork, and c) correct result using our method. }
%.
\label{fig:buddalion}
\end{figure}

%We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM. To prove both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity. We also compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.

We implemented our proposed method in C++, and tested a series of models on a laptop with an Intel Core i5 1.5 GHz CPU and 8 GB of RAM. To validate the efficiency and robustness of our method, we performed boolean evaluations on various CSGs with different complexities. We also compared our method with several existing methods, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact}, Cork  \cite{Cork}, QuickCSG \cite{douze2015quickcsg}, and Carve \cite{Carve}.

\subsection{Robustness \& Performance}

\begin{figure}[t]
\centering
\includegraphics[width=3in]{dual}
\caption{a) There is ambiguity as to the orientation of the loop in this tess-graph. b) When there is more than one connected component in a tess-graph, auxiliary intersections (yellow line) are used to connect the components.}
\label{fig:dual}
\end{figure}

\begin{table*}[ht]
\caption{Results of self-union evaluation using different methods}
\label{tab:selfunion}
\centering
\begin{tabular}{*{8}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
{No.} & {Model} & {Face Num.} &
CGAL & Maya & Cork & Carve & QuickCSG  & Our Method
\\
\hline\hline
1 & Ball & 360  & \cmark & \cmark & \xmark & \cmark & \xmark & \cmark \\
2 & Head & 2.7k& \cmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
3 & Bunny & 70k  & \xmark & \cmark & \xmark & \cmark & \xmark  & \cmark\\
4 & Dragon & 277k & \xmark & \xmark & \xmark & \xmark & \xmark  & \cmark \\
\hline
\end{tabular}
\begin{flushleft}
\end{flushleft}
\end{table*}

@@

@@

\vspace{0.5em}
\noindent\textbf{Seed label generation. }
The label vector of the seed vertex $\bm{\Lambda}(\bm{v}_0)$ can be generated by a point-in-polyhedron test \cite{ogayar2005point}, using the octree as an acceleration structure \cite{frisken2002simple}. However, a simpler strategy can be adopted which chooses a vertex with known labels as the seed. The inclusion labels of vertex with the maximum $x$-coordinate are either $out$ ($in$, if the complement is applied on the mesh) or $on$. The $on$ labels can be determined by connectivity. Exceptions can occur because of our ignorance of coplanar situations---vertices may not be added to the primitive, even if they are on surface of it. Fortunately, if seed vertex is chosen whose neighboring faces are not all coplanar, exceptions can be avoided.

@@

\vspace{0.5em}
\noindent\textbf{Exporting to float-point number. }
The vertices of the final mesh are represented as either planes or vertex coordinates. The vertices originating from the input meshes have exact coordinates, and the vertices newly introduced by the intersection between meshes have only P-reps, and require round-off when computing their coordinates. Although our method guarantees the correct topology in the final mesh, round-off errors can still cause topological deficiencies. This is called \textbf{vertex rounding} problem. We adopt the method of Zhou et al. \cite{zhou2016mesh} to solve this problem iteratively.

@@

We found that performance of our method was poor for CSGs that contained a lot of meshes within a small area (Table. \ref{tab:performance}, \emph{T1}). In these cases, our method computes many intersections that will not appear as edges in the final mesh, leading to unnecessary tessellation. Optimization may be explored to alleviate this problem.

The inputs of our method are limited to solids. However, recent reports have proposed that the piece-wise wind number (PWN) is a more powerful method to identify the insides and outsides of meshes \cite{zhou2016mesh}. The input requirements of our method may be extended to PWN meshes, that allow self-intersection. We believe that this would be an interesting and valuable extension of our work.

>>>>

\iffalse
\begin{figure}[t]
\centering
\includegraphics[width=3in]{perturb}
\caption{After perturbation, the self-union of \emph{Bunny} with QuickCSG still suffers from topology problem. The green boundary faces indicate topological deficiencies.}
%
\label{fig:boundaryedge}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3in]{buddalion}
\caption{ Results from $Budda\cup Lion$: a) incorrect result using CGAL, b) incorrect result using Cork, and c) correct result using our method. }
%.
\label{fig:buddalion}
\end{figure}
\fi
%We implemented the proposed method in C++ and tested a series of models on a laptop with Intel Core i5 1.5GHz CPU and 8GB RAM. To prove  both the efficiency and robustness, we perform boolean evaluation on various CSGs with different complexity. We also compared our method with several previous works with available implementations, including CGAL \cite{cgal:hk-bonp3-15a}, Maya \cite{Maya2015,barki2015exact},"Cork" \cite{Cork}, "QuickCSG" \cite{douze2015quickcsg}, "Carve" \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}.

We implemented our proposed method in C++, and tested a series of models on a PC with an Intel Core i5 CPU and 8 GB of RAM. We compared our method with several existing methods, including CGAL \cite{cgal:hk-bonp3-15a}, Cork  \cite{Cork}, QuickCSG \cite{douze2015quickcsg}, Carve \cite{Carve}, and online service of Campen and Kobbelt's plane-based method \cite{campen2010exact,WebBSP}. Among them, CGAL and Carve use exact arithmetic. To ensure fairness, we turn off any features of multi-thread computation during the comparison.
%Also, the self-intersection tests of meshes are performed using an open-source library VCG \cite{VCG}.

\subsection{Self-Union on Thingi10K Dataset}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{total3}
\caption{The performance of test on Thingi10k (top) and Barki et al.'s dataset (bottom). We outline the median of processing time for each method. The different histogram areas result from the different success rate.}
\label{fig:total}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{cleanness}
\caption{The result meshes of our method for the self-union of Thingi10k are cleaner than state-of-art methods. The Cork and QuickCSG assume general position and cannot handle self-union at all, so they failed to produce solids in most of the cases.}
\label{fig:cleanness}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{profile3}
\caption{Performance profile of tests on Thingi10k (top) and Barki et al.'s dataset (bottom). The red, yellow, green, blue areas represent the time percentage of octree construction, intersection computation, tessellation and classification, respectively. Each one-pixel column represents a test. All the tests are sorted by total processing time.}
\label{fig:profile}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3in]{scatter}
\caption{For the self-union tests on Thingi10k, the linear relation between processing time and triangle number is apparent.}
\label{fig:scatter}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.2in]{comp}
\caption{\emph{First row}: the results of self-union of \emph{components}. QuickCSG (adding perturbation of 1e-12) and Cork cannot produce valid results. CGAL and Carve simple crashed and do not give a result. \emph{Second row}: In our self-union tests, QuickCSG tends to produce results with many boundary edges (green lines), and Cork tends to produce many self-intersecting faces (red faces).}
\label{fig:perturb}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.0in]{boolean-11}
\caption{After coordinates approximation, the 'thin' triangle in the middle intersect adjacent faces and results in self-intersection on the mesh (red triangles).}
\label{fig:roundoff}
\end{figure}

We reproduce the experiments of \cite{zhou2016mesh} on the Thingi10K dataset on website thingiverse.com. The dataset currently contains 9956 .stl models, which are heavily biased towards 3D printing modeling by amateurs or semi-professionals. Since .stl models are triangle streams rather than meshes, we merge the exact coincident vertices to reconstruct connectivity. After that, we check the cleanness of all of the models. Among the 9956 meshes, 4509 meet the requirements of solid. The face numbers of these meshes generally follows a log-normal distribution with the average of 17k. We limit our comparison to these solid meshes.

The comparison results are available for CGAL, Cork, Carve and QuickCSG. Web service of Campen et al. \cite{campen2010exact,WebBSP} does not support batch processing. Therefore, we made a few tests manually, and roughly a half of them failed. The implementation of recent works \cite{zhou2016mesh,barki2015exact} are not available. Both methods are based on exact arithmetic. The performance of method in \cite{zhou2016mesh} is claimed to be close to Carve (with parallel computation) by the results on the same dataset Thingi10k in their paper.

The computation time of our method outperform most of other methods (see Fig. \ref{fig:total} \emph{top}). Even compared with the fastest QuickCSG, which is not exact, our method takes only about two times of the processing time. We profile each stage of our method, and the results indicate the bottleneck is the intersection computation (see Fig. \ref{fig:profile} \emph{top}). Also, from Fig. \ref{fig:scatter}, the linear relation between triangle number and processing time implies the ability of our method to handle large boolean evaluations.

Our method produces results in 98.8\% of the tests. The cleanness of resulting meshes are tested by checking self-intersecting (we use VCG \cite{VCG}) and the total signed incidence of every edge \cite{zhou2016mesh}. If the total signed incidence of every edge of a mesh is zero, then the mesh is a piecewise-constant
integer \emph{generalized winding number} (PWN) \cite{zhou2016mesh} mesh. These two requirements are sufficient conditions of solid. According to Fig. \ref{fig:cleanness}, over 80\% of our results are solids, which outperform all other methods. We also notice very low rates of success for Cork and QuickCSG. This is because both methods assume general position, which is not the case for self-union. Even after perturbation, they can hardly produce solid results (see Fig. \ref{fig:perturb}).

The failure cases and unclean results of our method do not impair the robustness of our algorithms. The reasons lie on the degenerate faces and close-to-degenerate faces from the inputs. The normal vectors of degenerate faces cannot be defined so face classification may fail when encounter such faces. Also, close-to-degenerate faces can become degenerate faces or lead to self-intersecting (see Fig. \ref{fig:roundoff}) after conversion to their P-reps. This is because the conversion method \cite{campen2010exact} requires coordinates rounding-off. In our implementation, the IEEE-754 single-precision floating-point coordinates (precision=24) are rounded to the precision of 18$\scriptsize{\sim}$20.

\subsection{Binary Boolean Operations}

\iffalse

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{boolean-06}
\caption{a) We construct an auxiliary connection to connect each inner component with outer component (the red line segment). By checking the intersections on the auxiliary connection, we find that the orange loops are identical.  b) We construct the P-rep of the auxiliary connection by $\bm{v}_o$ and the exact coordinates of the end points of $\bm{e}$. }
\label{fig:dual}
\end{figure}

@@

\vspace{0.5em}
\noindent\textbf{Seed label generation. }
The label vector of the seed vertex can be generated by a point-in-polyhedron test \cite{ogayar2005point}, using the octree as an acceleration structure \cite{frisken2002simple}. However, a simpler strategy can be adopted which chooses a vertex with known labels as the seed. The inclusion labels of vertex with the maximum $x$-coordinate are either $out$ ($in$, if the complement is applied on the mesh) or $on$. The $on$ labels can be determined by connectivity. Exceptions can occur because of our ignorance of coplanar situations---vertices may not be added to the primitive, even if they are on surface of it. Fortunately, if seed vertex is chosen whose neighboring faces are not all coplanar, exceptions can be avoided.

@@

\vspace{0.5em}
\noindent\textbf{Exporting to float-point number. }
The vertices of the final mesh are represented as either planes or vertex coordinates. The vertices originating from the input meshes have exact coordinates, and the vertices newly introduced by the intersection between meshes have only P-reps, and require round-off when computing their coordinates. Although our method guarantees the correct topology in the final mesh, round-off errors can still cause topological deficiencies. This is called \textbf{vertex rounding} problem. We can adopt the method of Zhou et al. \cite{zhou2016mesh} to solve this problem iteratively. For the consideration of efficiency, we do not include this step during our comparison experiments.

@@

We found that performance of our method was poor for CSGs that contained a lot of meshes within a small area (Table. \ref{tab:performance2}, \emph{T1}). In these cases, our method computes many intersections that will not appear as edges in the final mesh, leading to unnecessary tessellation. Optimization may be explored to alleviate this problem.

The inputs of our method are limited to solids. However, recent work \cite{zhou2016mesh} have proposed that the piecewise-constant integer \emph{generalized winding number} (PWN) is a more powerful method to identify the insides and outsides of meshes. The input requirements of our method may be extended to PWN meshes, that allow self-intersection. We believe that this would be an interesting and valuable extension of our work.

### 2017-03-06 tex/inter.tex
before merge with hongbo

\subsection{Space Division}
\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.2in]{octreediff}
\end{wrapfigure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{projection}
\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$. $Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$. The intersection between $t_1$ and $t_2$ (yellow line segment) is the overlap of $Seg_1$ and $Seg_2$.}
%Seg1 is the intersection between pt2,sp and t1. Seg2 is the intersection between pt1,sp and t2. The intersection between t1 and t2 (yellow line segment) is the overlap of Seg1 and Seg2.
\label{fig_projection}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=3in]{pbirep2}
\caption{The geometry of planes in a PBI-rep. The yellow line segment is the intersection represented by $\bm{\mathcal{I}}$.}
\label{fig:pbi}
\end{figure}

@@

In the first step, the computation of signed distances involves only the vertices coordinates and the supporting planes of triangles. Therefore, if the early rejections occur, the bounding planes are not needed at all. In addition, according to the conversion method of Campen et al.\cite{campen2010exact}, the supporting plane is represented by four double-precision floating-point numbers. The precisions of the first three parameters and the last parameter are $L_a$ and $L_d$ respectively. They hold the relation $L_d = L_a + L + 1$, where $L$ is the precision of the coordinates of input vertices. This means we can compute the signed distance exactly within double-precision. With these two facts, our early rejection is as fast as the vertex-based implementation.

If $t_1$ and $t_2$ are not coplanar, $Seg_1$ and $Seg_2$ are computed. The end points are intersections between the supporting plane of one triangle and an edge of the other triangle. By computing the bounding planes, the end points can be implicitly represented by plane triples, $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$, where $\bm{p}^i_{t_1, b}$ is the bounding plane of the related edge.
Fig. \ref{fig:isect} shows all of the possible intersection conditions between $t_1$ and $\bm{p}_{t_2, sp}$. The coplanar situation is discussed specifically in \S \ref{sec:degenerate}.

>>>>

\subsection{Space Division}
\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.2in]{boolean-10}
\end{wrapfigure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{boolean-12}
\caption{$Seg_1$ is the intersection between $\bm{p}_{t_2, sp}$ and $t_1$. $Seg_2$ is the intersection between $\bm{p}_{t_1, sp}$ and $t_2$. The intersection between $t_1$ and $t_2$ (red line segment) is the overlap of $Seg_1$ and $Seg_2$.}
%Seg1 is the intersection between pt2,sp and t1. Seg2 is the intersection between pt1,sp and t2. The intersection between t1 and t2 (yellow line segment) is the overlap of Seg1 and Seg2.
\label{fig_projection}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=3in]{boolean-13}
\caption{The geometry of planes in a PBI-rep. The red line segment ($\bm{\mathcal{I}}$) is the intersection represented by $\bm{\mathcal{I}}$.}
\label{fig:pbi}
\end{figure}

@@

In the first step, the computation of signed distances involves only the vertices coordinates and the supporting planes of triangles. Therefore, if the early rejections occur, the bounding planes are not needed at all. In addition, according to the conversion method of Campen et al.\cite{campen2010exact}, the supporting plane is represented by four double-precision floating-point numbers. The precisions of the first three parameters and the last parameter are $L_a$ and $L_d$ respectively. They hold the relation $L_d = L_a + L + 1$, where $L$ is the precision of the coordinates of input vertices. This means we can compute the signed distance exactly within double-precision. With these two facts, our early rejection does not involve plane-based computation, thus is very efficient.

If early rejection is not triggered and $t_1$ and $t_2$ are not coplanar, $Seg_1$ and $Seg_2$ are computed. The end points are intersections between the supporting plane of one triangle and an edge of the other triangle. By computing the bounding planes, the end points can be implicitly represented by plane triples, $\bm{p}_{t_2, sp} \cap \bm{p}_{t_1, sp} \cap \bm{p}^i_{t_1, b}$, where $\bm{p}^i_{t_1, b}$ is the bounding plane of the related edge.
Fig. \ref{fig:isect} shows all of the possible intersection conditions between $t_1$ and $\bm{p}_{t_2, sp}$. The coplanar situation is discussed specifically in \S \ref{sec:degenerate}.

### 2017-03-06 tex/intro.tex
before merge with hongbo

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry (CSG) is a widely used modeling tool. It constructs complex models by combining primitive solids with boolean operations. However, boolean evaluation, which computes the final model of CSG, has suffered from robustness problem for more than three decades. Some methods are fast but not robust, while some methods are robust but rely on exact arithmetic which is slow. Recent works tried to implement fast and robust boolean evaluation methods using plane-based representations (P-reps) of polyhedrons instead of vertex-based representations (V-reps) of polyhedrons. While they have achieved remarkable improvements, they are still slow compared with non-robust methods. We propose a fast and robust boolean method. It uses hybrid representations of polyhedrons, which combines P-reps with V-reps. It allows us to take advantages of both the efficiency of V-reps and the exactness of P-reps. Comparison experiments with the state-of-the-art show that our method is unconditionally robust for solid inputs, and is similarly efficient to existing non-robust methods.
\end{abstract}

@@

@@

Inspired by these previous studies, we develop a robust boolean method, which is unconditionally robust given consistent solid inputs, and as fast as non-robust methods. In our method, we combine P-reps with V-reps, forming hybrid representations of solids. Generally, the V-reps information is used for coarse tests and efficient neighboring face queries, while P-reps information is used for exact predicates. To avoid using exact arithmetic and ensure efficiency, we avoid constructions throughout our method.

Our method is different from the previous BSP-based methods \cite{bernstein2009fast,campen2010exact}.
While their methods are largely based on BSP theorem of \cite{naylor1990merging,thibault1987set}, our method is more like vertex-based methods such as \cite{feito2013fast,zhou2016mesh} and is significantly faster than these BSP-based methods. Our method is not a simple improvement of vertex-based methods, but a systematical solution for robustness of boolean evaluations. During intersection computation, we encode the triangle intersections into sets of planes, and then use these planes to determine exact tessellations. Subsequently, we classify each face in the tessellated meshes using small local BSP trees, which also compliment the P-reps to guarantee exactness. In order to guarantee performance, we try to minimize the usage of plane-based exact predicates in these stages. In addition, while most existing boolean methods can only process two meshes, our method is \textbf{variadic} \cite{zhou2016mesh}, which can evaluate arbitrary inputs immediately. Thus, our method may reduce evaluation time of large CSGs by avoiding repetitive computation. Experiments have shown that our method is much faster than existing robust methods, and only around two times slower than non-robust methods.

@@

Many researchers have attempted to solve the robustness issues using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean, zhou2016mesh,barki2015exact} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, these methods are too expensive in terms of computation time. For example, CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary} is more than 50 times slower than non-robust boolean operations \cite{bernstein2009fast}.

@@

The concept of plane-based representations (P-reps) of polyhedrons was first described by Sugihara and Iri \cite{sugihara1990solid}. By using P-reps, boolean evaluations can be performed with only predicates, which are much easier to implement robustly. Berstein and Fussell \cite{bernstein2009fast} combined P-reps with BSP trees \cite{thibault1987set,naylor1990merging} to develop a boolean method which is unconditionally robust with consistent inputs. Unlike vertex-based methods, their method does not rely on exact arithmetic to be robust.
However, the merging of two BSP trees is has $O(mn)$ time complexity, where $m$ and $n$ are the size of the trees. Such high time complexity makes this method impractical for large meshes. Subsequently, Campen and Kobbelt \cite{campen2010exact} improved this method by localizing BSP operations using an octree. In this method, mesh refinements only take place locally near intersections, which leads to better performance. However, their method splits the intersection regions and non-intersection regions, and requires extra stitching step to reconstruct topology. Also, the performance of localized BSP merging is still poor compared with the vertex-based methods.

>>>>

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry (CSG) is a widely used modeling tool. It constructs complex models by combining primitive solids with boolean operations. However, boolean evaluation, which computes the final model of CSG, has suffered from robustness problem for more than three decades. Some methods are fast but not robust, while some methods are robust but rely on exact arithmetic which is slow. Recent works tried to implement fast and robust boolean evaluation methods using plane-based representations (P-reps) of polyhedrons instead of vertex-based representations (V-reps) of polyhedrons. While they have achieved remarkable improvements, they are still slow compared with non-robust methods. We propose a fast and robust boolean method. It uses hybrid representations of polyhedrons, which combines P-reps with V-reps. The P-rep information is used for exact predicates computation and the V-rep information is used for coarse tests and fast topology query, which allows us to take advantages of both the efficiency of V-reps and the exactness of P-reps. Comparison experiments with the state-of-the-art show that our method is unconditionally robust for solid inputs, and is similarly efficient to existing non-robust methods.
\end{abstract}

@@

\begin{figure*}
  \centering
  \includegraphics[width=7in]{overview}
  \caption{The illustration of our framework for boolean evaluation using hybrid representations. Vertex-based computation has its advantage of efficiency, and plane-based is necessary to guarantee exact geometry predicates. }\label{fig:hybrid}
\end{figure*}

@@

Inspired by these previous studies, we develop a robust boolean method, which is unconditionally robust given consistent solid inputs, and is comparable efficient as non-robust methods. In our method, we combine P-reps with V-reps, forming hybrid representations of solids. Generally, the V-reps information is used for coarse tests and efficient neighboring face queries, while P-reps information is used for exact predicates (see Fig. \ref{fig:hybrid}). To avoid using exact arithmetic and ensure efficiency, we avoid constructions throughout our method.

Our method is different from the previous BSP-based methods \cite{bernstein2009fast,campen2010exact}.
While their methods are largely based on BSP theorem of \cite{naylor1990merging,thibault1987set}, our method is more like vertex-based methods such as \cite{feito2013fast,zhou2016mesh} and is significantly faster than these BSP-based methods. Our method is not a simple improvement of vertex-based methods, but a systematical solution for robustness of boolean evaluations. During intersection computation, we encode the triangle intersections into sets of planes, and then use these planes to determine exact tessellations. Subsequently, we classify each face in the tessellated meshes using small local BSP trees, which also compliment the P-reps to guarantee exactness. In order to guarantee performance, we try to minimize the usage of plane-based exact predicates in these stages. In addition, while most existing boolean methods can only process two meshes in each time, our method is \textbf{variadic} \cite{zhou2016mesh}, which can evaluate boolean expression with multiple input meshes immediately. Thus, our method reduce evaluation time of large CSGs by avoiding repetitive computation. Experiments have shown that our method is much faster than existing robust methods, and only around two times slower than non-robust methods.

@@

On the other hand, some methods focus on robustness. The state-of-art method \cite{zhou2016mesh} try to handle a large range of topology deficiencies and guarantee to give solid outputs, with the cost of many extra computations such as self-intersecting test and vertex-rounding iterations.
As robustness problem results from numerical errors, many researchers have attempted use arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean, zhou2016mesh,barki2015exact} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, exact arithmetic are too expensive in terms of computation time. For example, CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary} is more than 50 times slower than non-robust boolean operations \cite{bernstein2009fast}. Our method try to balance the performance and robustness, which guarantees the solid outputs under valid inputs without the use of exact arithmetic.

@@

The concept of plane-based representations (P-reps) of polyhedrons was first described by Sugihara and Iri \cite{sugihara1990solid}. By using P-reps, boolean evaluations can be performed with only predicates, which are much easier to implement robustly. Berstein and Fussell \cite{bernstein2009fast} combined P-reps with BSP trees \cite{thibault1987set,naylor1990merging} to develop a boolean method which is unconditionally robust with consistent inputs. Unlike vertex-based methods, their method does not rely on exact arithmetic to be robust.
However, the merging of two BSP trees is has $O(mn)$ time complexity, where $m$ and $n$ are the size of the trees. Such high time complexity makes this method impractical for large meshes. Subsequently, Campen and Kobbelt \cite{campen2010exact} improved this method by localizing BSP operations using an octree. In this method, mesh refinements only take place locally near intersections, which leads to better performance. However, their method splits the intersection regions and non-intersection regions, and requires extra stitching step to reconstruct topology. Also, the performance of localized BSP merging is still poor compared with the vertex-based methods. Our method uses plane-based geometry to guarantee no error introduced during boolean evaluation, while reduces the performance impact from plane-based computation with V-reps information, which is much cheaper to use.

### 2017-03-06 tex/overview.tex
before merge with hongbo

\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.5 in]{p-reps}
\end{wrapfigure}

@@

Under P-reps, vertex is represented with a much higher precision than under V-reps. A plane is represented by four parameters. Then a vertex takes twelve parameters under P-reps compared with only three parameters under V-reps. This makes geometric computations significantly slower under P-reps. Even though numerical filters can be applied to speed up, pure plane-based methods, such as \cite{sugihara1990solid,banerjee1996topologically}, cannot be as fast as vertex-based methods. On the other hand, a hybrid representation may bring both the efficiency of V-reps and the exactness of P-reps. And plane-based geometric computation should be avoided as much as possible to reduce computation cost.

@@

\begin{figure}
  \centering
  \includegraphics[width=3.5in]{twopointoneline}\\
  \caption{Geometric configuration of the linear ordering of points. Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$. We convert this problem into the plane ordering of $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
\end{figure}

\noindent Given a line $\bm{l}_{ab}$ with two points on it, $\bm{v}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1\cap\bm{p}_a^2)$, and $\bm{v}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1\cap\bm{p}_b^2)$, we need to determine the linear order of the two points along $\bm{l}_{ab}$ (see Fig. \ref{fig:twopointoneline}).
To solve this problem, we choose one plane that is not parallel with $\bm{l}_{ab}$ from the P-rep of each point, then convert this problem into one of determining the linear order of planes, which can be solved using the method of Banerjee et al. \cite{banerjee1996topologically}. The chosen planes should have the same orientation with respect to $\bm{l}_{ab}$ (the dot product between the plane normal and $\bm{l}_{ab}$ must be positive), and unqualified planes need to be flipped.

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{circularorder}
\caption{Geometric configuration of the circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are within plane $\bm{p}_0$.}
%Geometric configuration of the circular ordering of lines. la:
\label{fig:circularorder}
\end{figure}

>>>>

\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.5 in]{boolean-07}
\end{wrapfigure}

@@

Under P-reps, vertex is represented with a much higher precision than under V-reps. A plane is represented by four parameters. Then a vertex takes twelve parameters under P-reps compared with only three parameters under V-reps. This makes geometric computations significantly slower under P-reps. Even though numerical filters can be applied to speed up, pure plane-based methods, such as \cite{sugihara1990solid,banerjee1996topologically}, are significant slower than vertex-based methods. On the other hand, a hybrid representation can bring both the efficiency of V-reps and the exactness of P-reps. And plane-based geometric computation should be avoided as much as possible to reduce computation cost.

@@

\begin{figure}
  \centering
  \includegraphics[width=3.5in]{boolean-09}\\
  \caption{Geometric configuration of the linear ordering of points. Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$. We convert this problem into the plane ordering of $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
\end{figure}

\noindent Given a line $\bm{l}$ with two points on it, $\bm{v}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1\cap\bm{p}_a^2)$, and $\bm{v}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1\cap\bm{p}_b^2)$, we need to determine the linear order of the two points along $\bm{l}$ (see Fig. \ref{fig:twopointoneline}).
To solve this problem, we choose one plane that is not parallel with $\bm{l}$ from the P-rep of each point, then convert this problem into one of determining the linear order of planes, which can be solved using the method of Banerjee et al. \cite{banerjee1996topologically}. The chosen planes should have the same orientation with respect to $\bm{l}$ (the dot product between the plane normal and $\bm{l}$ must be positive), and unqualified planes need to be flipped.

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{boolean-08}
\caption{Geometric configuration of the circular ordering of lines. $\bm{l}_a\colon(\bm{p}_0 \cap \bm{p}_a)$ and $\bm{l}_b\colon(\bm{p}_0 \cap \bm{p}_b)$ are within plane $\bm{p}_0$.}
%Geometric configuration of the circular ordering of lines. la:
\label{fig:circularorder}
\end{figure}
